Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters

### 2023-06-26 report/report.tex
still working on report

\section{Related Work}
\color{red}
\begin{itemize}
    \item General stuff about Saarland's economy and its market segments?
    \item How market segments are normally identified?
    \item Theory behind business clusters and maybe related work?
    \item Related Work on clustering in economy?
    \item Mention that we collected traditional economic data?
\end{itemize}
\color{black}
\nm{Related work for business stuff is still missing! Also adjust motivation for embeddings?}

@@

\section{Results}
\nm{Move current clustering results to appendix and rewrite section for the new results, keep location recommendation results as they are?}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/clustering_results.png}
    \caption{Clustering of company descriptions using t-SNE and Agglomerative clustering. The company descriptions and industries were used as features.}
    \label{fig:t-sne-agglomerative}
\end{figure}

In this section, we will investigate the results of the best-performing configuration of our clustering and location recommendation system. These results were obtained using the following configuration: the description embeddings were computed using max pooling, the embeddings were projected into 2D space using t-SNE, and the clustering was achieved using Agglomerative clustering. We found that this configuration yields the most sensible predictions of market segments and location recommendations. Figure \hyperref[fig:t-sne-agglomerative]{$2$} displays the resulting clustered data points, and the plots of the other configurations can be found in the appendix.

@@

\appendix
\nm{Upload all LaTeX files to overleaf when its done since they want a link! Update readme in repo!}
\begin{itemize}
	\item \textbf{Link to Code}: Provide the link to your code repository. You can use any service to host your code (Github, gdrive etc.). The code should be running, accessible and all of your work must be reproducible. In case your code is not accessible or not in a working state, relevant number of points will be deducted.   
	\item \textbf{Link to Overleaf}: Add a link to the Overleaf project which contains all of the LaTex related files for this report.
	\item \textbf{Additional Figures}: Add any and all additional figures produced during you work with relevant explanations in the appendix.
\end{itemize}

>>>>

\section{Related Work}
\color{red}
\begin{itemize}
    \item General stuff about Saarland's economy and its market segments?
    \item How market segments are normally identified?
    \item Theory behind business clusters and maybe related work?
    \item Related Work on clustering in economy?
    \item Mention that we collected traditional economic data?
\end{itemize}
\color{black}
\nm{Related work for business stuff is still missing!}

@@

\section{Results}
\nm{Rewrite clustering section for the new results, keep location recommendation results as they are?}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/clustering_results.png}
    \caption{Clustering of company descriptions using t-SNE and Agglomerative clustering. The company descriptions and industries were used as features.}
    \label{fig:t-sne-agglomerative}
\end{figure}

In this section, we will investigate the results of the best-performing configuration of our clustering and location recommendation system. These results were obtained using the following configuration: the description embeddings were computed using max pooling, the embeddings were projected into 2D space using t-SNE, and the clustering was achieved using Agglomerative clustering. We also used the companies' industry as an additional feature.
 We found that this configuration yields the most sensible predictions of market segments and location recommendations. Figure \ref{fig:t-sne-agglomerative} displays the resulting clustered data points.

@@

\appendix
\nm{Upload all \LaTeX{} files to overleaf when its done since they want a link! Update readme in repo!}
\begin{itemize}
	\item \textbf{Link to Code}: Provide the link to your code repository. You can use any service to host your code (Github, gdrive etc.). The code should be running, accessible and all of your work must be reproducible. In case your code is not accessible or not in a working state, relevant number of points will be deducted.   
	\item \textbf{Link to Overleaf}: Add a link to the Overleaf project which contains all of the LaTex related files for this report.
	\item \textbf{Additional Figures}: Add any and all additional figures produced during you work with relevant explanations in the appendix.
\end{itemize}
